# Results

```{r}
# Add libraries and read in data
library(readr)
library(dplyr)
library(naniar)   # For missing data visualization and summaries
library(visdat)
library(ggplot2)
library(tidyr)
library(ggmosaic)
library(stringr)


atusAllGroups2023 <- read_csv("data/atusAllGroups2023.csv", show_col_types = FALSE)

MedianWeeklyEarningByPresenceOfChildren <- read_csv("data/MedianWeeklyEarningByPresenceOfChildrenTable7.csv", show_col_types = FALSE)
MedianWeeklyEarningByRace <- read_csv("data/MedianWeeklyEarningByRaceTable18.csv", show_col_types = FALSE)
MedianWeeklyEarningsByGenderEducation <- read_csv("data/MedianWeeklyEarningsByGenderEducationTable24.csv", show_col_types = FALSE)
MedianHourlyEarningsHispanicByAge <- read_csv("data/MedianHourlyEarningsHispanicByAgeTable25.csv", show_col_types = FALSE)
MedianHoursWorkedByRaceGender <- read_csv("data/MedianHoursWorkedByRaceGenderTable26.csv", show_col_types = FALSE)

MedianWeeklyEarningsByOccupation <- read_csv("data/MedianWeeklyEarningsByOccupation.csv", show_col_types = FALSE)
MedianWeeklyEarningsByOccupationAggregate <- read_csv("data/MedianWeeklyEarningsByOccupationAggregate.csv", show_col_types = FALSE)

MedianWeeklyEarningsByMaritalStatus <- read_csv("data/MedianWeeklyEarningsByMaritalStatus.csv", show_col_types = FALSE)


```

# Occupation: The Primary Driver of the Gender Wage Gap

One of the most significant factors driving the gender wage gap is occupation. Men and women tend to be concentrated in different types of jobs, and these occupations vary greatly in terms of pay. Occupations that are predominantly female, such as nursing, teaching, and caregiving, tend to be lower-paying compared to male-dominated fields like technology, finance, and management.

In this section, we will discuss the occupations men and women chose and the earnings imbalance within those occupations. This will help provide a clear picture of how much the gender wage gap varies depending on the field.

## Total Earnings by Gender and Occupation Group

In this plot, we see total earnings across women and men (created by multiplying male/female median earnings for each occupation by the number of male/female workers in that occupation). This gives us a sense of what total women earnings and total male earnings come from.

We see more of the share of management, business, and financial wages go to men, and a hgiher share of the education, healthcare, and office occupations go to men. 


```{r}

library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)  # For label formatting

# Prepare the data
data_clean <- MedianWeeklyEarningsByOccupation |>
  filter(total_number_of_workers >= 15, 
         !is.na(men_median_weekly_earnings) & !is.na(women_median_weekly_earnings))

# Calculate total earnings by multiplying median weekly earnings by the number of workers
data_clean <- data_clean |>
  mutate(men_total_earnings = men_median_weekly_earnings * men_number_of_workers,
         women_total_earnings = women_median_weekly_earnings * women_number_of_workers)

# Reshape the data to long format for stacking
data_long <- data_clean |>
  dplyr::select(occupation, occupation_group_major, men_total_earnings, women_total_earnings) |>
  pivot_longer(cols = c(men_total_earnings, women_total_earnings),
               names_to = "gender",
               values_to = "total_earnings") |>
  mutate(gender = recode(gender, 
                        "men_total_earnings" = "Men", 
                        "women_total_earnings" = "Women"))

# Create stacked bar chart with color by major occupation group
ggplot(data_long, aes(x = gender, y = total_earnings, fill = occupation_group_major)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Total Earnings by Gender and Occupation Group",
       x = "Gender",
       y = "Total Earnings (Billions)",
       fill = "Occupation Group") +
  scale_fill_brewer(palette = "Set3") +  # Use a color palette for different occupation groups
  # use 1e-6 for billions bc no. of workers in thousands already
  scale_y_continuous(labels = label_number(scale = 1e-6, suffix = "B")) +  # Format Y-axis in billions
  theme_minimal() +
  theme(legend.position = "right")  # Place the legend to the right


```


## Comparing Earnings and Representation: Cleveland Dot Plot
To dig a little deeper, we can also examine the number of workers in each occupation alongside median weekly earnings for men and women. The following Cleveland dot plot helps visualize both the earnings disparity and the gender representation within each occupation. It shows the median earnings for both men and women, and how the size of the workforce differs between genders.

This comparison reveals that while some high-paying occupations, like management and engineering, have larger numbers of men than women, women are often clustered in lower-paying, high-population fields, such as office support and education roles. The imbalance in gender representation, combined with the pay differences, exacerbates the overall wage gap.

```{r}
# Reshape the data to long format
data_long <- MedianWeeklyEarningsByOccupationAggregate |>
  dplyr::select(occupation, men_number_of_workers, women_number_of_workers, men_median_weekly_earnings, women_median_weekly_earnings) |>
  pivot_longer(cols = c(men_number_of_workers, women_number_of_workers, men_median_weekly_earnings, women_median_weekly_earnings), 
               names_to = "variable", values_to = "value") |>
  mutate(gender = case_when(
    str_detect(variable, "women") ~ "Women",
    str_detect(variable, "men") ~ "Men"
  ),
  variable = case_when(
    str_detect(variable, "number_of_workers") ~ "Number of Workers",
    str_detect(variable, "median_weekly_earnings") ~ "Median Weekly Earnings"
  ))

# Plot with both number of workers and median weekly earnings
ggplot(data_long, aes(x = value, y = occupation, color = gender)) +
  geom_point(size = 4) +
  facet_wrap(~ variable, scales = "free_x") +  # Separate by the variable (Workers vs Earnings)
  scale_color_manual(values = c("blue", "pink")) +
  labs(title = "Number of Workers and Median Weekly Earnings by Occupation (Men vs Women)",
       x = "Value", 
       y = "Occupation",
       color = "Gender") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8))  # Adjust y-axis labels for readability

```


Further, let's look at the top occupations for men and women, and what the gender imbalance looks like in each.

```{r}

# Load necessary libraries
library(dplyr)
library(ggplot2)

# Assuming data is loaded into MedianWeeklyEarningsByOccupation
data <- MedianWeeklyEarningsByOccupation

# Clean data by removing NA values for men's and women's earnings
data_clean <- data |>
  filter(!is.na(men_median_weekly_earnings) & !is.na(women_median_weekly_earnings)) |>
  mutate(
    wage_gap = (women_median_weekly_earnings / men_median_weekly_earnings) * 100
  )

# Top 15 Occupations by Number of Women Workers (sorted by number of workers)
top_15_women <- data_clean |>
  arrange(desc(women_number_of_workers)) |>
  head(15) |>
  mutate(occupation = factor(occupation, levels = rev(occupation))) |>
  select(occupation, women_number_of_workers, wage_gap)

# Top 15 Occupations by Number of Men Workers (sorted by number of workers)
top_15_men <- data_clean |>
  arrange(desc(men_number_of_workers)) |>
  head(15) |>
  mutate(occupation = factor(occupation, levels = rev(occupation))) |>
  select(occupation, men_number_of_workers, wage_gap)

# Plot for Top 15 Occupations by Women Workers (sorted by number of workers)
p1 <- ggplot(top_15_women, aes(x = occupation, y = wage_gap, fill = wage_gap)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(wage_gap, 1), "%")), 
            vjust = 0.5, color = "white", fontface = "bold") +  # Add labels inside bars
  coord_flip() + # Flip the axes for readability
  labs(
    title = "Wage Gap for Top 15 Occupations by Number of Women Workers",
    x = "Occupation",
    y = "Wage Gap (%)"
  ) +
  scale_fill_gradient(low = "red", high = "blue") +  # Red for lower wage gap, Green for higher wage gap
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

# Plot for Top 15 Occupations by Men Workers (sorted by number of workers)
p2 <- ggplot(top_15_men, aes(x = occupation, y = wage_gap, fill = wage_gap)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(wage_gap, 1), "%")), 
            vjust = 0.5, color = "white", fontface = "bold") +  # Add labels inside bars
  coord_flip() + # Flip the axes for readability
  labs(
    title = "Wage Gap for Top 15 Occupations by Number of Men Workers",
    x = "Occupation",
    y = "Wage Gap (%)"
  ) +
  scale_fill_gradient(low = "red", high = "blue") +  # Red for lower wage gap, Green for higher wage gap
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

# Print both plots
p1
p2

```

## Men’s vs. Women’s Weekly Earnings: Scatter Plot By Occupation

When we compare men’s and women’s weekly earnings directly, we can see how the gap plays out across different occupations. The scatter plot below shows men’s weekly earnings on the x-axis and women’s weekly earnings on the y-axis. Each point represents a different occupation, and the 45-degree line acts as the "equality line," where men and women would be earning the same amount.

From this chart, it’s clear that the majority of occupations fall below the equality line, showing that men earn more than women in most job categories. However, there are a few occupations that have closer parity, especially in fields like arts and healthcare where the gender balance is somewhat more equitable. Still, overall, the data reflects the persistent gap between male and female earnings across most sectors.


```{r}
library(plotly)
library(dplyr)

# Clean the data
data_clean <- MedianWeeklyEarningsByOccupation |>
  filter(total_number_of_workers >= 15, 
         !is.na(men_median_weekly_earnings) & !is.na(women_median_weekly_earnings))

# Create the scatter plot using plot_ly
plot_ly(data = data_clean, 
        x = ~men_median_weekly_earnings, 
        y = ~women_median_weekly_earnings, 
        type = 'scatter', 
        mode = 'markers', 
        text = ~occupation,  # Hover text with occupation names
        hoverinfo = 'text',  # Show only occupation on hover
        color = ~occupation_group_major,  # Color by occupation group
        colors = c("red", "blue", "green", "orange"),  # Specify colors for groups
        marker = list(size = 10, opacity = 0.7)) |>
  layout(
    title = "Men vs. Women Median Weekly Earnings by Occupation",
    xaxis = list(title = "Men's Median Weekly Earnings ($)"),
    yaxis = list(title = "Women's Median Weekly Earnings ($)"),
    shapes = list(
      # Add 45-degree line (y = x) as a reference
      list(
        type = "line", 
        x0 = 500, x1 = max(data_clean$men_median_weekly_earnings, na.rm = TRUE), 
        y0 = 500, y1 = max(data_clean$women_median_weekly_earnings, na.rm = TRUE), 
        line = list(color = "black", width = 2, dash = "dot")
      )
    ),
    annotations = list(
      # Add annotation outside the chart
      list(
        x = 1.1,  # Position outside the plot area (right side)
        y = .05,     # Position vertically at the top of the chart
        xref = "paper",  # Use 'paper' to position relative to plot area
        yref = "paper",  # Use 'paper' to position relative to plot area
        text = "---- Men Median Pay = Women Median Pay", 
        showarrow = TRUE,
        arrowhead = 2, 
        ax = 20, 
        ay = 0,   # Adjust arrow direction to point to the line
        font = list(size = 12, color = "black")
      )
    )
  )

```


# Familial Status: The Impact of Marriage and Children

Beyond occupation, marital and familial status also significantly impact the gender wage gap. Women, particularly those with children, often face challenges that men do not. The unequal division of household and caregiving responsibilities means that women may have to reduce their working hours or step out of the workforce entirely to care for children or manage household chores. This often leads to fewer opportunities for career advancement and lower wages overall.


## Marital Status and the Wage Gap: Women’s Earnings by Marital Status
Let’s now look at the impact of marital status on women’s wages. This bar chart shows women’s median weekly earnings as a percentage of men’s earnings, broken down by marital status.

The data reveals that never-married women earn significantly more than their married counterparts. This may be because they do not face traditional household and caregiving demands. Divorced and widowed women also tend to earn more than married women, possibly because they have taken on greater financial independence and responsibility after major life transitions, driving them to pursue higher-paying opportunities.

Married women tend to experience a larger wage gap and seperated women experience the largest. One possibility for this may be family responsibilities limitting their career opportunities. This highlights how family structure continues to impact women’s wages, with unmarried women facing fewer barriers to higher pay.


```{r}
# Assuming the data is loaded into `MedianWeeklyEarningsByMaritalStatus`
data <- MedianWeeklyEarningsByMaritalStatus

# Calculate women's earnings as a percentage of men's earnings
data$women_as_percent_of_men = (data$women_median_weekly_earnings / data$men_median_weekly_earnings) * 100

# Reorder MaritalStatus factor based on women_as_percent_of_men in descending order
data$MaritalStatus <- reorder(data$MaritalStatus, -data$women_as_percent_of_men)

# Plot: Women's Earnings as a Percentage of Men's Earnings with Labels
ggplot(data, aes(x = MaritalStatus, y = women_as_percent_of_men, fill = MaritalStatus)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_text(aes(label = paste0(round(women_as_percent_of_men, 1), "%")), 
            vjust = 1.5, color = "white", fontface = "bold") +  # Add '%' and adjust label position
  labs(
    title = "Women's Median Weekly Earnings as Percentage of Men's Earnings by Marital Status",
    x = "Marital Status",
    y = "Women's Earnings as % of Men's Earnings"
  ) +
  theme_grey() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## The Impact of Children: Women’s Earnings by Parental Status
Next, we focus on parental status and its effect on women’s wages. This bar chart compares women’s earnings as a percentage of men’s across different categories of parental status, including women with no children, women with children under 6, and women with children 6-17 years old.

The data shows a clear trend: women with children under the age of 6 experience the greatest wage disparity, earning far less than men in similar occupations. This likely reflects the additional caregiving responsibilities that come with raising young children. Women with older children still face a wage gap, but it is somewhat smaller, suggesting that the impact of children on women’s wages is most pronounced during the early years of child-rearing.


```{r}
data <- MedianWeeklyEarningByPresenceOfChildren |>
  filter(Characteristic != "With children under 18 years old")

women_data <- data |>
  filter(Gender == "Women") |>
  select(Marital_Status, Characteristic, women_median_weekly_earnings = Median_weekly_earnings)

men_data <- data  |>
  filter(Gender == "Men")  |>
  select(Marital_Status, Characteristic, men_median_weekly_earnings = Median_weekly_earnings)

# Join women and men data by Marital_Status and Characteristic
merged_data <- left_join(women_data, men_data, by = c("Marital_Status", "Characteristic"))

# Calculate women's earnings as a percentage of men's earnings
merged_data <- merged_data |>
  mutate(women_as_percent_of_men = (women_median_weekly_earnings / men_median_weekly_earnings) * 100)

# Remove rows with missing data (if any)
merged_data <- merged_data  |>
  filter(!is.na(women_as_percent_of_men))

# Reorder the 'Characteristic' factor levels to ensure the bars appear in the correct order
merged_data$Characteristic <- factor(merged_data$Characteristic, 
                                     levels = c("Total", 
                                                "With no children under 18 years old", 
                                                "With children under 6 years old", 
                                                "With children 6 to 17 none younger"))

# Plot: Women's Earnings as a Percentage of Men's Earnings by Children Status, without legend and with simplified x-axis
ggplot(merged_data, aes(x = Characteristic, y = women_as_percent_of_men, fill = Characteristic)) +
  geom_bar(stat = "identity", position = "dodge", show.legend = FALSE) +  # Remove legend
  geom_text(aes(label = paste0(round(women_as_percent_of_men, 1), "%")), 
            vjust = 1.5, color = "white", fontface = "bold", size=3) +  # Add percentage labels
  labs(
    title = "Women's Median Weekly Earnings as Percentage of Men's Earnings by Children Status",
    x = "Children Status",
    y = "Women's Earnings as % of Men's Earnings"
  ) +
  scale_x_discrete(labels = function(x) gsub(":", "\n", x)) +  # Add line breaks in x-axis labels
  theme_minimal() +  # Clean theme
  theme(axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better visibility
        axis.ticks.x = element_blank(),  # Hide x-axis ticks
        axis.title.x = element_text(size = 12),  # Set title size for x-axis
        axis.title.y = element_text(size = 12),  # Set title size for y-axis
        legend.position = "none") +  # Ensure no legend is shown
  facet_wrap(~ Marital_Status, scales = "free_y")

```

## Unpaid Labor and Time Allocation: Insights from the American Time Use Survey

One crucial but often overlooked factor contributing to the gender wage gap is the unequal distribution of unpaid labor, particularly in the form of household chores and childcare. The American Time Use Survey (ATUS) provides valuable data on how individuals allocate their time across various activities each day. By comparing the daily schedules of men and women, we can see how these differences in time use impact their earnings.

In the following bar chart, we break down the average 24-hour weekday activities for both men and women. The data reveals a significant disparity in how men and women spend their time: women consistently spend more hours on unpaid tasks such as housework and childcare, while men tend to allocate more time to leisure and paid work.

This unequal time allocation has serious implications for the wage gap. Women’s additional hours spent on unpaid labor mean they have less time for paid work or career advancement. This imbalance in household responsibilities contributes directly to the wage disparity, as women often face more career interruptions or constraints due to their caregiving roles.

By highlighting the everyday time trade-offs that women make, this chart underscores the structural challenges that prevent women from fully participating in the workforce, ultimately affecting their long-term earning potential.

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(grid)


# Reshape the data into a long format
atus_long <- atusAllGroups2023 |>
  pivot_longer(cols = starts_with("AnyChildren") | starts_with("NoChildren"), 
               names_to = "Group_Gender", values_to = "Time") |>
  separate(Group_Gender, into = c("Group", "Gender"), sep = "_") |>
  filter(Gender %in% c("Men", "Women")) |>
  mutate(Group = factor(Group, levels = c("AnyChildrenUnder18", "NoChildren")),
         Gender = factor(Gender, levels = c("Men", "Women")),
         Major_Activity_Group = factor(Major_Activity_Group, levels = unique(Major_Activity_Group)),
         Activity = factor(Activity, levels = unique(Activity))) |>
  # Sum the time by Major_Activity_Group for each Group and Gender
  group_by(Major_Activity_Group, Group, Gender) |>
  summarise(Total_Time = sum(Time, na.rm = TRUE)) |>
  ungroup() |>
  # Normalize the total time to 24 hours
  group_by(Group, Gender) |>
  mutate(Time = Total_Time / sum(Total_Time) * 24) |>
  ungroup()

atus_long <- atus_long |>
  mutate(Group_Gender = factor(interaction(Group, Gender), 
                               levels = c("NoChildren_Men", "NoChildren_Women", "AnyChildrenUnder18_Men", "AnyChildrenUnder18_Women")))

# Calculate percentages for each stacked segment
atus_long <- atus_long |>
  group_by(Group_Gender) |>
  mutate(Percentage = Time / sum(Time) * 100) |>
  ungroup()


# Create a horizontal stacked bar chart with ggplot2
ggplot(atus_long, aes(x = Time, y = interaction(Gender, Group), fill = Major_Activity_Group)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Set3") +  # Color palette for the activities
  labs(x = "Time (hours)", y = "Group & Gender", title = "Time Spent by Activity (24-Hour Breakdown)") +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 0),  # Keep y-axis labels horizontal
        legend.position = "bottom") +
  scale_y_discrete(labels = c("Men, Children Under 18", "Women, Children Under 18",
                              "Men, No Children", "Women, No Children")) +
  guides(fill = guide_legend(title = "Activity")) +
  # Set the x-axis limit to 24 hours and ensure the last label is 24
  scale_x_continuous(breaks = seq(0, 24, by = 4), limits = c(0, 24.01), expand = c(0, 0)) +
  # Add percentages to each segment
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), color = "black", size = 3)

```


# Hours Worked and Earnings by Gender and Race

Notes: Hours worked is kinda messy, looks like white families have the lowest %; Median earnings looks like Black and Hispanic have noticeably higher %s compared to White/Asian, however once you plot the dollar values of earnings (of men) we see that Black and Hispanic groups have consistently made much less than asian/white over time.


```{r}

# Filter for Year>=2000 due to Asian data not being collected until then
tabRaceGenderHoursWorked <- filter(MedianHoursWorkedByRaceGender, Year>=2000)
tabRaceGenderEarnings <- filter(MedianWeeklyEarningByRace, (Year>=2000) & (Year<2023))

# Some data manipulation to get it ready for plotting
tabRGHours_t <- tabRaceGenderHoursWorked |> select(-Total16Plus) |>
  pivot_longer( 
    cols=c("White","Black_or_African_American","Asian","Hispanic_or_Latino_ethnicity"),
    names_to = "Race", values_to = "HoursWorked")
tabRGHours_t <- pivot_wider(tabRGHours_t, names_from=Gender, values_from=HoursWorked)
tabRGHours_t$women_as_percent_of_men = (tabRGHours_t$Women / tabRGHours_t$Men) * 100

tabRGEarnings_t <- tabRaceGenderEarnings |> select(-Total) |>
  pivot_longer(
    cols=c("White","Black_or_African_American","Asian","Hispanic_or_Latino_ethnicity"),
    names_to = "Race", values_to = "Earnings")
tabRGEarnings_t <- pivot_wider(tabRGEarnings_t, names_from=Gender, values_from=Earnings)
tabRGEarnings_t$women_as_percent_of_men = (tabRGEarnings_t$Women / tabRGEarnings_t$Men) * 100

# Plot hours worked data
ggplot(data=tabRGHours_t, aes(x=Year, y=women_as_percent_of_men, group=Race)) +
  geom_line(aes(color = Race)) +
  geom_point(aes(color = Race)) +
  labs(
    title = "Women's Median Hours Worked as Percentage of Men's by Race",
    x = "Year",
    y = "Women's Hours Worked as % of Men's"
  ) +
  theme_light()

# Plot earnings data
ggplot(data=tabRGEarnings_t, aes(x=Year, y=women_as_percent_of_men, group=Race)) +
  geom_line(aes(color = Race)) +
  geom_point(aes(color = Race)) +
  labs(
    title = "Women's Median Earnings as Percentage of Men's by Race",
    x = "Year",
    y = "Women's Earnings as % of Men's"
  ) +
  theme_light()

# Plot earnings data
ggplot(data=tabRGEarnings_t, aes(x=Year, y=Men, group=Race)) +
  geom_line(aes(color = Race)) +
  geom_point(aes(color = Race)) +
  labs(
    title = "Men's Median Earnings by Race",
    x = "Year",
    y = "Median Earnings"
  ) +
  theme_light()
```




```{r}

# Example data for men and women
years <- seq(-2, 18, by = 2)  # X-axis values (Years Since Birth of First Child)
men <- c(-4, 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.2)  # Y-axis values for Men
women <- c(-4, 0, -1.5, -1.2, -1, -0.8, -0.6, -0.4, -0.2, 0, 0.1)  # Y-axis values for Women


years

# Create the plot
plot(
  years, men, type = "o", pch = 16, lty = 1, col = "black", ylim = c(-4, 4.5),
  xlab = "Years Since Birth of First Child", ylab = "", 
  main = "Effects of Birth on Earnings Over Time by Gender", 
  xaxt = "n", yaxt = "n", bty = "n"
)

# Add gridlines
abline(h = seq(-4, 4, by = 1), col = "gray90", lwd = 0.5)
abline(v = seq(-2, 18, by = 2), col = "gray90", lwd = 0.5)

# Add the lines and points for women
lines(years, women, type = "o", pch = 17, lty = 2, col = "gray50")

# Add axes
axis(1, at = seq(-2, 18, by = 2), labels = seq(-2, 18, by = 2))
axis(2, at = seq(-4, 4, by = 1), labels = seq(-4, 4, by = 1), las = 1)

# Add legend
legend(
  "bottomright", legend = c("Men", "Women"), 
  pch = c(16, 17), lty = c(1, 2), col = c("black", "gray50"), 
  bty = "n", cex = 0.9
)


```
